Calculating Entropies With Nested Sampling

### 2017-02-08 paper/ms.tex
Bit of work on the intro

\section{Introduction}

If an unknown quantity $\x$ has a discrete probability distribution $p(\x)$,
the entropy is
\begin{align}
H_{\x} &= -\sum_{\x} p(\x) \log p(\x)
\end{align}
where the sum is over all of the possible values of $\x$ under consideration.
This probability distribution is implicitly conditional on some prior
information, which is have omitted from the notation.

@@

Bayesian inference is the use of probability theory to
describe uncertainty, often about unknown quantities
(``parameters'') $\x$. Some data $\d$, initially unknown but
thought to be relevant to $\x$, is obtained.
The prior information leads the
user to specify a prior distribution $p(\x)$ for the unknown parameters,
along with a ``sampling distribution'' $p(\d | \x)$ describing prior knowledge
of how the data is related to the parameters
(i.e., if the parameters where known, what data would likely be observed?). By the product rule, this yields a {\em joint prior}
\begin{align}
p(\x, \d) &= p(\x)p(\d | \x)
\end{align}
which is the starting point for inference.

>>>>

\section{Introduction}
\noindent
If an unknown quantity $x$ has a discrete probability distribution $p(x)$,
the Shannon entropy \citep{shannon} is defined as
\begin{align}
H_{x} &= -\sum_{x} p(x) \log p(x)
\end{align}
where the sum is over all of the possible values of $x$ under consideration.
Throughout this paper, I use the compact
`overloaded' notation for probability distributions, writing $p(x)$ instead
of the more cumbersome $P(X=x)$.
This probability distribution is implicitly conditional on some prior
information, which has been omitted from the notation.

\citet{knuth} has shown that the entropy quantifies the degree to which the
question ``which value of $x$ is true?'' remains unanswered by the prior
information.

@@

Bayesian inference is the use of probability theory to
describe uncertainty, often about unknown quantities
(``parameters'') $\x$. Some data $\d$, initially unknown but
thought to be relevant to $\x$, is obtained.
The prior information leads the
user to specify a prior distribution $p(\x)$ for the unknown parameters,
along with a ``sampling distribution'' $p(\d | \x)$ describing prior knowledge
of how the data is related to the parameters
(i.e., if the parameters where known, what data would likely be observed?). By the product rule, this yields a {\em joint prior}
\begin{align}
p(\x, \d) &= p(\x)p(\d | \x)
\end{align}
which is the starting point for inference \citep{caticha}.
